Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-02-26 paper.tex
Changed plots, updating pdf

\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}

@@

The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1987}.  Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{Lemaire}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{Lemaire}, \cite{Moldwin}, \cite{OBrien}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.

\cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.  \vnote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.  \vnote{What did they find/conclude?}

\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \vnote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.  \vnote{What did they find/conclude?}

@@

\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \vnote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$. The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.  The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.

>>>>

\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}
\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

@@

The plasma trough is the transition region between the high density and low temperature plasmasphere and the lower density and, in the equatorial plane, higher energy magnetosphere \citep{Mayr1968ModelMagnetosphereTemperature}.  Although there are well--validated models of the plasmasphere density as a function of $L$ (\cite{Gallagher1988EmpiricalModelPlasmasphere}, \cite{LemaireEarthsPlasmasphere}, \cite{Takahashi2006}, and \cite{Takahashi2010}) and plasmapause boundaries (\cite{LemaireEarthsPlasmasphere}, \cite{Moldwin2002ModelPlasmapause}, \cite{OBrien2003EmpiricalPlasmapause}), the dependence of the plasma trough on solar wind conditions has not been extensively studied.

\cite{Gallagher1988EmpiricalModelPlasmasphere} modeled the the plasmasphere as a simple linear fit dependent on $L$ shell, geographic altitude, geomagnetic latitude, and $K_p$.  \inote{What was major finding?} \cite{Hamilton1988RingCurrentDevelopment} analyzed a strong geomagnetic storm and compared energy measurements of the ring current to $D_{st}$, along with measurements of ring current compositions before, during, and after the storm.  \inote{What did they find/conclude?}

\cite{Lotoaniu1999PlasmaMassDensity} used measurements from the \inote{???} instrument on the CRRES sateelite and compared in-situ measured plasma mass density to that inferred by ground-based ULF wave measurements that extended to the plasmatrough.  \inote{What did they find/conclude?}

@@

\cite{Takahashi2010} developed a mass density dataset using measurements from the SEM \inote{Check instrument} instruments on the GOES satellites from 1980 through 1992, with most measurements in the range $L=6.8\pm0.2 R_E$. The mass density $\rho$ was estimated using the the Alf\v'en wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.  The equatorial mass density, $\rho_{eq}$, was derived from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.
